\documentclass[11pt]{article}
\usepackage[a4paper, margin=1in]{geometry}
\usepackage{graphicx}
\usepackage{xcolor}
\usepackage{hyperref}
\usepackage{enumitem}
\usepackage{fontawesome}
\usepackage{tcolorbox}
\usepackage{fancyhdr}
\usepackage{tabularx}
\usepackage{booktabs}

% Define colors
\definecolor{primary}{RGB}{0, 123, 255}
\definecolor{secondary}{RGB}{108, 117, 125}
\definecolor{success}{RGB}{40, 167, 69}
\definecolor{dark}{RGB}{50, 54, 66}

% Set up hyperlinks
\hypersetup{
    colorlinks=true,
    linkcolor=primary,
    urlcolor=primary,
}

% Set up headers and footers
\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\fancyfoot[C]{\thepage}
\fancyhead[L]{\textcolor{primary}{Cybersecurity Hackathon}}
\fancyhead[R]{\textcolor{primary}{Fall 2025}}

% Custom commands
\newcommand{\sectiontitle}[1]{
    \vspace{0.3cm}
    \noindent\textcolor{primary}{\Large\textbf{#1}}
    \vspace{0.2cm}
}

\newcommand{\eventitem}[2]{
    \noindent\textbf{#1} \hfill #2\\
}

\begin{document}

\begin{center}
    \vspace*{-1cm}
    \textcolor{primary}{\Huge\textbf{CYBERSECURITY HACKATHON}}\\
    \vspace{0.5cm}
    \textcolor{primary}{\Large\textbf{48-HOUR CHALLENGE FOR SECURITY ENTHUSIASTS}}\\
    \vspace{0.3cm}
    \textcolor{secondary}{\large Fall 2025 • Craiova / Bucharest}\\
    \vspace{0.5cm}
    {\normalsize June 1, 2025}\\
    \vspace{0.8cm}
\end{center}

% Image temporarily removed due to format issues

\begin{tcolorbox}[colback=primary!10, colframe=primary, title=\textbf{Event Overview}]
The Cybersecurity Hackathon is a 48-hour challenge where participants work in teams to solve real-world cybersecurity problems. Open to security enthusiasts of all levels, from beginners to experts, this event provides a platform to develop and showcase your skills while networking with industry professionals.

\textit{Note: Details, dates, and themes are subject to change.}
\end{tcolorbox}

\sectiontitle{Challenge Format}

Teams of 2-4 participants will tackle a series of increasingly difficult cybersecurity challenges across multiple domains. The event combines elements of Capture The Flag (CTF) competitions with practical security implementation scenarios that mirror real-world situations.

\sectiontitle{Challenge Categories}

\begin{itemize}[leftmargin=*]
    \item \textbf{Web Application Security}: Identify and exploit vulnerabilities in web applications
    \item \textbf{Network Security}: Analyze and secure network infrastructure
    \item \textbf{Cryptography}: Break and implement cryptographic systems
    \item \textbf{Reverse Engineering}: Analyze compiled applications to understand their functionality
    \item \textbf{Forensics}: Investigate digital evidence to reconstruct security incidents
    \item \textbf{Social Engineering}: Develop strategies to counter social engineering attacks
\end{itemize}

\sectiontitle{Schedule}

\textbf{Day 1:}
\begin{tabularx}{\textwidth}{lX}
\toprule
\textbf{Time} & \textbf{Activity} \\
\midrule
08:00 - 09:00 & Registration and Check-in \\
09:00 - 10:00 & Opening Ceremony and Challenge Briefing \\
10:00 - 12:00 & Team Formation and Strategy Session \\
12:00 - 13:00 & Lunch \\
13:00 - 18:00 & Hacking Session \\
18:00 - 19:00 & Dinner \\
19:00 - 22:00 & Evening Workshop: "Advanced Exploitation Techniques" \\
22:00 - 08:00 & Overnight Hacking (Optional) \\
\bottomrule
\end{tabularx}

\vspace{0.5cm}

\textbf{Day 2:}
\begin{tabularx}{\textwidth}{lX}
\toprule
\textbf{Time} & \textbf{Activity} \\
\midrule
08:00 - 09:00 & Breakfast \\
09:00 - 12:00 & Continued Hacking Session \\
12:00 - 13:00 & Lunch \\
13:00 - 15:00 & Final Hacking Sprint \\
15:00 - 16:00 & Solution Submission Deadline \\
16:00 - 17:30 & Team Presentations \\
17:30 - 18:30 & Judging and Deliberation \\
18:30 - 20:00 & Awards Ceremony and Closing \\
\bottomrule
\end{tabularx}

\sectiontitle{Prizes and Recognition}

\begin{itemize}[leftmargin=*]
    \item \textbf{First Place}: Mentorship opportunities with leading cybersecurity firms
    \item \textbf{Second Place}: Premium security tools licenses
    \item \textbf{Third Place}: Security conference tickets
    \item \textbf{Category Winners}: Special recognition in each challenge category
    \item \textbf{Most Innovative Solution}: Special award for the most creative approach
\end{itemize}

\sectiontitle{Who Should Participate}

\begin{itemize}[leftmargin=*]
    \item Security professionals looking to sharpen their skills
    \item Computer science students interested in cybersecurity careers
    \item Software developers wanting to improve their security knowledge
    \item IT professionals seeking to enhance their security capabilities
    \item Security researchers and enthusiasts of all levels
\end{itemize}

\sectiontitle{Registration Information}

Registration opens soon. Early registration is encouraged as participation is limited to 100 participants (25-30 teams) to ensure quality mentoring and support.

\begin{tcolorbox}[colback=success!10, colframe=success, title=\textbf{Ready to Learn More?}]
Join us for an intense 48-hour hackathon that will challenge your abilities and connect you with the cybersecurity community.

Visit our website to browse cybersecurity courses: \href{https://chen.ist/academy/courses.html}{chen.ist/academy/courses.html}
\end{tcolorbox}

\sectiontitle{Frequently Asked Questions}

\textbf{Do I need to be a cybersecurity expert to participate?}\\
No, we welcome participants of all skill levels. Teams are encouraged to include members with diverse experience levels, and mentors will be available to assist throughout the event.

\textbf{What should I bring?}\\
Participants should bring their own laptops, chargers, and any preferred peripherals. We'll provide power, high-speed internet, and a comfortable workspace.

\textbf{Is there a participation fee?}\\
Details soon. All meals and materials during the event are covered by our sponsors.

\textbf{Will accommodation be provided?}\\
Accommodation is not included, but we have arranged special rates with nearby hotels. Details will be provided to registered participants.

\textbf{Can I participate remotely?}\\
This hackathon is designed as an in-person event to maximize collaboration and mentorship opportunities. Remote participation is not available.

\vspace{1cm}
\begin{center}
    \textbf{For more information and updates:}\\
    \vspace{0.3cm}
    Visit \href{https://chen.ist/academy/programs/hackathons/cybersecurity-hackathon}{chen.ist/academy/programs/hackathons/cybersecurity-hackathon}\\
    \vspace{0.3cm}
    Contact: \texttt{contact@chen.ist}
\end{center}

\end{document}